---
title: "read_in_from_web"
author: "Courtney Johnson"
date: "October 9, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

Find his themes

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
library(httr)
library(rvest)
library(ggridges)

theme_set(theme_bw() + theme(legend.position = "bottom"))

```


```{r}
nyc_airbnb = read_csv("./nyc_airbnb.csv")
View(nyc_airbnb)
```

Rename / clean some things

```{r}
nyc_airbnb = nyc_airbnb %>%
  mutate(stars = review_scores_location / 2) %>%
  rename(boro = neighbourhood_group)
```

```{r}
nyc_airbnb %>%
  count(boro, neighbourhood) %>% View
```

## Some questions
* Does rating very by neighbourhood, room type, or both?
* How is price related to other variables?
* Where are rentals located?

* What's the most expensive area? What about the least?
* Which listings have the most unfilled days?
* Which area has the highest density of listings?
* What are some host characteristics? How many listings? What's associatetd with ratings?


#### Does rating very by neighbourhood, room type, or both?

```{r}
nyc_airbnb %>%
  group_by(neighbourhood) %>% 
  summarize(median(stars, na.rm = TRUE)) %>% View

nyc_airbnb %>%
  group_by(room_type) %>%
  summarize(median(stars, na.rm = TRUE), n = n()) %>% View

nyc_airbnb %>%
  group_by(boro, room_type) %>%
  summarize(
    mean_stars = mean(stars, na.rm = TRUE)
  ) %>% 
  spread(key = room_type, value = mean_stars) %>% View

ggplot(nyc_airbnb, aes(x = stars), color = boro) + 
  geom_histogram() +
  facet_grid(~room_type)
```


#### Where are rentals located?

```{r}
plot_1 = nyc_airbnb %>%
  ggplot(aes(x = longitude, y = latitude, color = boro)) + 
  geom_point() +
  viridis::scale_color_viridis(discrete = TRUE)
plot_1

plot_2 = nyc_airbnb %>%
  filter(boro == "Manhattan", price > 1000) %>%
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = 0.2) +
  facet_grid(~room_type) +
  viridis::scale_color_viridis() 
plot_2
```

#### What's the most expensive area?


```{r}
table_1 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Brooklyn") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  top_n(5) %>%
  knitr::kable(digits = 1)
table_1

table_2 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  top_n(5) %>%
  knitr::kable(digits = 1)
table_2

table_3 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  top_n(-5) %>%
  knitr::kable(digits = 1)
table_3

table_4 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  arrange(mean_price) %>%
  knitr::kable(digits = 1)
table_4
```


## October 11 Lecture

### Scrape a table


First get the HTML 

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_xml = read_html(url)

drug_use_xml
```

Get the first table from the HTML (%>% .[[1]]) 
(This gives the same result as the following code chunk)

```{r}
drug_use_xml %>%
  html_nodes(css = "table") %>%
  .[[1]] %>%
  html_table() %>%
  slice(-1) %>%
  as_tibble() %>% View
```


```{r}

table_marj = (drug_use_xml %>% html_nodes(css = "table"))[[1]] %>%
  html_table()  %>%
  .[-1,] %>% 
  as_tibble()

table_marj
```


### Learning Assessment
 
Extract table from cost of living of nyc page

```{r}
url2 = "https://www.bestplaces.net/cost_of_living/city/new_york/new_york"

cost_of_living = read_html(url2)

nyc_COL = cost_of_living %>%
  html_nodes(css = "table") %>%
  .[[1]] %>%
  html_table(header = TRUE) 

nyc_COL
```

### Harry Potter

```{r}
hpsaga_html = read_html("https://www.imdb.com/list/ls000630791/")

titles = hpsaga_html %>%
  html_nodes(css = ".lister-item-header a") %>%
  html_text()

money = hpsaga_html %>%
  html_nodes(css = ".text-muted .ghost~ .text-muted+ span") %>%
  html_text()

hpsaga_df = tibble(
  title = titles,
  gross_rev = money
)

```


### Napoleon Dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

```


### Water Consumption

Get the water data 

```{r}
nyc_water = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.csv") %>% 
  content("parsed")
```

As JSON

```{r}
nyc_water_json = GET("https://data.cityofnewyork.us/resource/waf7-5gvc.json") %>%
  content("text") %>%
  jsonlite::fromJSON() %>%
  as_tibble()
```

### BRFSS

```{r}
brfss_smart2010 = 
  GET("https://data.cdc.gov/api/views/acme-vg9e/rows.csv?accessType=DOWNLOAD") %>% 
  content("parsed")
```

### Pokemon

```{r}
poke = GET("http://pokeapi.co/api/v2/pokemon/1") %>%
  content()
```




