---
title: "read_in_from_web"
author: "Courtney Johnson"
date: "October 9, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

Find his themes

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
library(httr)
library(ggridges)

theme_set(theme_bw() + theme(legend.position = "bottom"))

```


```{r}
nyc_airbnb = read_csv("./nyc_airbnb.csv")
View(nyc_airbnb)
```

Rename / clean some things

```{r}
nyc_airbnb = nyc_airbnb %>%
  mutate(stars = review_scores_location / 2) %>%
  rename(boro = neighbourhood_group)
```

```{r}
nyc_airbnb %>%
  count(boro, neighbourhood) %>% View
```

## Some questions
* Does rating very by neighbourhood, room type, or both?
* How is price related to other variables?
* Where are rentals located?

* What's the most expensive area? What about the least?
* Which listings have the most unfilled days?
* Which area has the highest density of listings?
* What are some host characteristics? How many listings? What's associatetd with ratings?


#### Does rating very by neighbourhood, room type, or both?

```{r}
nyc_airbnb %>%
  group_by(neighbourhood) %>% 
  summarize(median(stars, na.rm = TRUE)) %>% View

nyc_airbnb %>%
  group_by(room_type) %>%
  summarize(median(stars, na.rm = TRUE), n = n()) %>% View

nyc_airbnb %>%
  group_by(boro, room_type) %>%
  summarize(
    mean_stars = mean(stars, na.rm = TRUE)
  ) %>% 
  spread(key = room_type, value = mean_stars) %>% View

ggplot(nyc_airbnb, aes(x = stars), color = boro) + 
  geom_histogram() +
  facet_grid(~room_type)
```


#### Where are rentals located?

```{r}
plot_1 = nyc_airbnb %>%
  ggplot(aes(x = longitude, y = latitude, color = boro)) + 
  geom_point() +
  viridis::scale_color_viridis(discrete = TRUE)
plot_1

plot_2 = nyc_airbnb %>%
  filter(boro == "Manhattan", price > 1000) %>%
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = 0.2) +
  facet_grid(~room_type) +
  viridis::scale_color_viridis() 
plot_2
```

#### What's the most expensive area?


```{r}
table_1 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Brooklyn") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  top_n(5) %>%
  knitr::kable(digits = 1)
table_1

table_2 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  top_n(5) %>%
  knitr::kable(digits = 1)
table_2

table_3 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  top_n(-5) %>%
  knitr::kable(digits = 1)
table_3

table_4 = nyc_airbnb %>%
  select(boro, neighbourhood, price) %>%
  filter(boro == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(n_listings = n(),
            mean_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE)
            ) %>%
  arrange(mean_price) %>%
  knitr::kable(digits = 1)
table_4
```






